A new type of automated prover based on category theory

### 2022-08-15 paper.tex
speed boost for xelatex

\documentclass{article}

\usepackage{amsmath, amssymb, graphics, setspace}	%% for maths display
\usepackage[letterpaper, total={6.5in, 9in}]{geometry}	%% set paper size & margin
\usepackage{cite}	%% for citations
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usetikzlibrary{positioning, cd, arrows}	%% for comutative diagram & flowchart drawing

\newcommand{\mathsym}[1]{{}}	%% generated by mma
\newcommand{\unicode}[1]{{}}	%% generated by mma
\newtheorem{theorem}{Theorem}	%% definition for theorem env
\newtheorem{axiom}{Axiom}	%% definition for axiom env
\newtheorem{definition}{Definition}	%% definition for definition env

@@

\setlength{\parskip}{0.8em}	%% set white space between paragraphs

@@

\title{A new type of automated prover based on category theory}
\author{Zijian Wang}
\date{\today}	%% compile date
\maketitle

\begin{center}
Northeast Yucai School, Shenyang, Liaoning, P.R.China
\end{center}

\hrule %% horizonal line
\begin{abstract}
In this article a new type of automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
and new algorithms is presented. The brackets provide an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given.
\end{abstract}
\hrule	%% horizonal line

\section{Introduction}
During the long period of development of the research on automated theorem provers, there have already existed a great number of research and implementation on proofs focusing on a specific mathematical subject, such as algebra equations (for example, Wolfram Mathematica{'}s FindEquationProof function \cite{2}) or geometrical theorems (for example, the Geometry Expert or GEX \cite{3} of Key Laboratory of Mathematics Mechanization, Chinese Academy of Sciences). Some relatively new works in this aspect includes Microsoft{'}s Lean prover \cite{8} and Z3 \cite{9} algorithm.

@@

Mainly developed in the twentieth century by the contribution of MacLane and Eilenberg with the purpose to investigate algebra topology, the category theory is a fast-evolving aspect of modern mathematics. In just a few decades, the category theory has become the standard and formal language of homology algebra and algebraic geometry and has gained a lot of meaningful achievements, for instance the Yoneda{'}s Lemma and Braid categories, which serves as a neat explanation for the Yang-Baxter Equation (YBE) \cite{1}. Moreover, the category theory{'}s main idea, which is to put mathematical structures into categories satisfies the worldview of the Bourbaki school.

@@

\[f: A\to B\]
\[x\mapsto y\]

@@

To avoid misunderstandings, \textbf{the Zermelo-Fraenkel set theory} or ZFC as short is utilized to be the set system, with Grothendieck universe concepts added. \cite{1}

@@

The definitions and theories presented in the paper utilizes the concepts of the category theory \cite{1} and axiomatic set theory \cite{1}. Therefore, readers are recommended to review understandings and conclusions about the two concepts before going over the paper.

@@

%%\pmb{ Theorem. }
\begin{theorem}
	The Zermelo{'}s Well-Ordering Theorem.\cite{1}

@@

	The proof can be found in citation \cite{1}.
\end{theorem}

Some preliminary knowledge also includes the Ebbinghaus Forgetting Curve equation \cite{4} used in this paper later. This approximate function is defined below:

\[E(\mathit{t})=\frac{100 k}{(\ln  t)^c+k}\]

@@

So as to avoid utilization of impure functions, a pseudo random generator is used. We select the linear congruential generators \cite{5}, whose recursive equation is,

\[X_{n+1}=(\left(a X_n+c\right) \bmod M)\]

@@

\[M=2^{32},a=1103515245, c=12345\]

@@

\section{The Computerized Representation of Mathematical Structures}

Before more specific discussion, we select Grothendieck universe \(\mathcal{U}\) \cite{1} to avoid set theory paradoxes. Besides, we define meta category \(\mathcal{C}\) where all discussions take place. There are briefly three kind of objects in \(\mathcal{C}\): symbols, notations and brackets. All symbols in \(\mathcal{C}\) forms sub-category \(\text{Sym}(\mathcal{C})\) called the \textbf{ Symbol Subcategory}. All notations in \(\mathcal{C}\) forms \(\text{Not}(\mathcal{C})\) and all brackets forms \(\text{Bra}(\mathcal{C})\), called the \textbf{ Notation Subcategory} and the \textbf{ Bracket Subcategory}. That is,

\[\mathcal{C}=\text{Sym}(\mathcal{C})\sqcup \text{Not}(\mathcal{C})\sqcup \text{Bra}(\mathcal{C})\]

@@

	\[\beta \text{:=}\left\{(i,x)\left|i\in \text{On}_{\geq 1}\right.,x\in \text{Sym}(\mathcal{C})\cup \text{Not}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\right\}\]

@@

	\[\beta =\{(j,\mathcal{N})\}\cup \left\{(i,x)\left|i\in \text{On}_{\geq 1}\right., x\in \text{Sym}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\right\},\forall
	t\in \beta ,j\in \text{On}_{\left[1,t_{\ell }\right]}\]
\end{definition}

@@

	\[\mathit{p}:\text{Ob}(\text{Not}(\mathcal{C}))\to \text{On}_{\geq 0}\]
	\[\mathcal{N}\overset{\mathit{p}}{\mapsto }n\]

@@

	\[\nu :\text{Sym}(\mathcal{C})\to \text{Not}(\mathcal{C})\]
	\[\mathcal{S}\overset{\mathit{v}}{\mapsto }\nu (\mathcal{S})\]

	\noindent where \(\nu (\mathcal{S})\) is the \textbf{ corresponding notation} of \(\mathcal{S}\) and must satisfy \(\forall \mathcal{S}\in \text{Sym}(\mathcal{C}),\mathit{p}(\nu (\mathcal{S}))=0\), indicating all corresponding notations are types instead of operators. For convenience and precision, the text that meaning creating a symbol \(\mathcal{S}\) whose corresponding notation is \(\mathcal{N}\)can and should be written in the form below.

	\[\mathcal{S}\in \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\mathcal{S})==\mathcal{N}\]

@@

	\[\epsilon :\alpha \equiv \beta\]
\end{definition}

A bracket, in order to enhance simplicity, can be wrapped into a symbol. Therefore with these three definitions, how do we actually represent mathematical stuff? One example is how to utilize them to express one of the most basic mathematical concepts, such as a single number 12. To complete this task, we may first define a notation Number and define a symbol \(\mathcal{S}_1\) whose corresponding notation is Number. Then, how do we determine the number is 12 instead of other numbers like 15? This can be solved using the ordinal theory we presented before in the Preliminary section.

@@

	\[h\in \text{Mor}(\text{Not}(\mathcal{C})): \mathcal{M}\to \mathcal{N}\]

	It is obviously without any ambiguity that \(\forall \mathcal{M},\mathcal{N}\in \text{Not}(\mathcal{C}),\left|\text{Hom}_{\mathcal{C}}(\mathcal{M},\mathcal{N})\right|\in \{0,1\}\). Moreover, if \(\mathcal{N}\) is a kind of \(\mathcal{M}\) then \(\mathit{p}(\mathcal{N})\geq \mathit{p}(\mathcal{M})\). For simplicity, \(\mathcal{N}\) is inherited from \(\mathcal{M}\) can be annotated as \(\mathcal{N}\triangleleft |\mathcal{M}\).
\end{definition}

@@

\[\sum _{n=0}^{\infty } x^n=\frac{1}{1-x}, \text{for} |x|<1\]

First, we need to observe what notation is needed by the construction. Apparently, we need to at least define these notations: \(\text{infinity}\), \(\text{integer}\), \(\text{number}\),\textit{  }\textit{ \(\sum\)}, \(=\), \({}^{\wedge}\), \(/\), \(-\), \(\text{abs}\), \(<\) and \(\text{for}\), where \(\text{abs}\) stands for the absolute value function. However, in this neat example, the concept of function is not needed to be defined. Additionally, as the constructed stuff only needs to demonstrate the equation itself instead of the principles behind the equality, there is no necessity for the definition of notation \(+\). Note that manifestly \(\text{integer} \triangleleft | \text{number}\). The table below demonstrates the number of parameters taken by the notations.

\begin{table}
	\centering
	\begin{tabular}{ccccccccccc}
		\toprule
		$\mathcal{N}$ & integer & number & infinity & $\sum$ & $=$ & $/$ & - & abs & $<$ & for \\
		\midrule
		$\mathit{p} (\mathcal{N})$ & $0$ & $0$ & $0$ & $3$ & $2$ & $2$ & $2$ & $1$ & $2$ & $2$ \\
		\bottomrule
	\end{tabular}
	\caption{The table for $\mathit{p}(\mathcal{N})$}
\end{table}

@@

\[\pmb{1}\in \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{1})=\text{number}\]
\[\pmb{\infty }\in \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{\infty })=\text{infinity}\]
\[\pmb{x}\in \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{x})=\text{number}\]
\[\pmb{n}\in \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{n})=\text{integer}\triangleleft |\text{number}\]
\[\alpha =\{(0,\text{for}),(1,\beta ),(2,\gamma )\}\]
\[\beta =\{(0,=),(1,\delta ),(2,\epsilon )\}\]
\[\gamma =\{(0,<),(1,\zeta ),(2,\pmb{1})\}\]
\[\delta =\{(0,\sum ),(1,\eta ),(2,\pmb{\infty }), (3,\theta )\}\]
\[\epsilon =\{(0,/),(1,\pmb{1}),(2,\iota )\}\]
\[\zeta =\{(0,\text{abs}),(1,\pmb{x})\}\]
\[\eta =\{(0,=),(1,\pmb{n}),(2,\pmb{1}\pmb{)}\pmb{\}}\]
\[\theta =\{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\}\]
\[\iota =\{(0,-),(1,\pmb{1}),(2,\pmb{x})\}\]

@@

\[\alpha =\{(0,\text{for}),(1,\beta ),(2,\{(0,<),(1,\{(0,\text{abs}),(1,\pmb{x})\}),(2,\pmb{1})\})\}\]
\[\beta =\{(0,=),(1,\delta ),(2,\{(0,/),(1,\pmb{1}),(2,\{(0,-),(1,\pmb{1}),(2,\pmb{x})\})\})\}\]
\[\delta =\{(0,\sum ),(1,\{(0,=),(1,\pmb{n}),(2,\pmb{1})\}),(2,\pmb{\infty }), (3,\{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\})\}\]

@@

	It is essential to pay attention to that a bracket with 2-parameter notation is not necessarily a micro-statement. This conclusion can be illustrated via the example of \(\{(0,+),(1,x),(2,y)\}\) whose notation has two symbols as parameters but is not a micro-statement. The second restriction is more important, which is that a micro-statement must have the capacity to be evaluated into a Boolean value, that is, \(\text{true}\) or \(\text{false}\). What is notable, the \textbf{ evaluation} process is not declared inside the representation system, whose definition comes below. All micro-statement brackets forms the \textbf{ Micro-Statement }sub-category of \(\text{Bra}(\mathcal{C})\) and is annotated as \(\text{Mic}(\mathcal{C})\).
\end{definition}

@@

	\[\mathit{e}\mathit{v}\mathit{a}\ell :\text{Ob}(\text{Mic}(\mathcal{C}))\to \mathcal{B}\]
	\[\mathit{m}\overset{\mathit{e}\mathit{v}\mathit{a}\ell }{\mapsto }\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})\]

@@

\[\forall \alpha ,\beta \in \text{Ob}(\text{Mic}(\mathcal{C})), \forall \left|\text{Hom}_{\text{Mic}(\mathcal{C})}(\alpha ,\beta )\right|=1\]

@@

	\[\mathcal{D}\text{:=}\left\{\left(i,\mathcal{M}_i\right)|i\in \text{On}_{\geq 1}\right\}\]

@@

	\[\left(i,\mathcal{M}_i\right)\overset{\mathit{s}\mathit{t}\mathit{e}\mathit{p}}{\mapsto }\left(i+1,\mathcal{M}_{i+1}\right)\]

@@

	\[\mathcal{M}_{i+1}=\mathcal{F}_i\mathcal{M}_i\]
\end{definition}

@@

	\[\exists n\in [0,\omega ), \mathcal{R}\subseteq \text{Ob}\left(\mathcal{M}_n\right)\]

@@

	\[\sigma =T(\mathcal{K})_{\ell }\]
	\[\tau =T(\mathcal{K})_{\mathit{r}}\]
\end{definition}

@@

	\[\text{Ts}\text{:=}\left\{t\in \mathcal{M}_i|t\simeq T(\mathcal{K})_{\ell }\right\}\]
\end{definition}

@@

	\[\mathcal{T}:\alpha _{\mathcal{B}}\cup \alpha _{\mathcal{S}}\to \beta _{\mathcal{B}}\cup \beta _{\mathcal{S}}\]
	\[\mathcal{S}_1\overset{\mathcal{T}}{\mapsto }\mathcal{S}_2\]

@@

	\[(\mu ')_{\mathcal{B}}\cup (\mu ')_{\mathcal{S}} =\mathcal{T}^{-1}\left(\mu _{\mathcal{B}}\cup \mu _{\mathcal{S}}\right)\]

	And then micro-statement \(\mu '\) is the freshly baked derivation achievement. All of the micro-statements as results of map \(\mathcal{T}^{-1}\) forms new set \(\mathcal{M}'\). In the end we process the pool \(\mathcal{M}\) with this union operation:

@@

\[\mathcal{K}_n\overset{k_n}{\to }\mathcal{K}_{n+1}, n\in \mathbb{Z}_{[0,N-1]}\]
\[\mathcal{K}_N\overset{k_N}{\to }\mathcal{K}_0\]

Graphically, we have:

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[commutative diagrams/every diagram]
		\node (K0) at (90:2.3cm) {$\mathcal{K}_0$};
		\node (K1) at (90+72:2cm) {$\mathcal{K}_1$};
		\node (K2) at (90+2*72:2cm) {$\mathcal{K}_2$};
		\node (K3) at (90+3*72:2cm) {$\mathcal{K}_3$};
		\node (Kn) at (90+4*72:2cm) {$\mathcal{K}_N$};

@@

		\path[commutative diagrams/.cd, every arrow, every label, dashed]
		(K3) edge node {$K_3$} (Kn)
		(Kn) edge node {$k_N$} (K0);
\end{tikzpicture}
	\caption{The initial map.}
\end{figure}

@@

	\[w = k_j\left(\mathcal{K}_j\right)\]

@@

	\[w = (\mathit{r} \bmod \sum _{u=0}^N )\left|\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_j,\mathcal{K}_q\right)\right|\]

	It is easy to understand that for each reflection functor \(\mathcal{K}_a\) and \(\mathcal{K}_b\), the count of set \(\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_a,\mathcal{K}_b\right)\) indicates the \textbf{ weight} of \(\mathcal{K}_b\) to \(\mathcal{K}_a\), controlling the probability of \(\mathcal{K}_b\) to be selected when the former functor is \(\mathcal{K}_a\). The design of this process is inspired by the lottery scheduling algorithm I learned in Andrew S. Tanenbaum{'}s Operating Systems: Design and Implementation \cite{6} before.
\end{definition}

An issue that worth attention is that as the random generator is defined as the following recursion formula: \cite{5}

\[X_{n+1}=(\left(1103515245 X_n+12345\right) \bmod 2^{32})\]

>>>>

\documentclass[preprint]{elsarticle}

\hfuzz=2pt
\special{dvipdfmx:config z 0} %% speed boost

%% \usepackage[letterpaper, total={5.3in, 9in}]{geometry}	%% set paper size & margin
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution

\usetikzlibrary{positioning, cd, arrows}	%% for comutative diagram & flowchart drawing

\newtheorem{theorem}{Theorem}	%% definition for theorem env
\newtheorem{axiom}{Axiom}	%% definition for axiom env
\newdefinition{definition}{Definition}	%% definition for definition env

@@

%% \setlength{\parskip}{0.8em}	%% set white space between paragraphs

@@

\title{A new type of automated prover based on category theory}
\author[1]{Zijian Wang\fnref{fn1}}
\ead{felix_wzj@yahoo.com}
\ead[url]{zijianfelixwang.github.io}

\fntext[fn1]{Author conducting the research, student of the Northeast Yucai School of P.R.China}

\affiliation[1]{organization={Northeast Yucai School},addressline={Shiji Rd. 41, Hunnan},city={Shenyang},postcode={110000},country={P.R.China}}
\maketitle

\begin{abstract}
In this article a new type of automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
and new algorithms is presented. The brackets provide an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given.
\end{abstract}

\begin{keyword}
	automatic prover \sep theorem prover \sep algorithm \sep category theory \sep provers \sep statement prover
\end{keyword}

\section{Introduction}
During the long period of development of the research on automated theorem provers, there have already existed a great number of research and implementation on proofs focusing on a specific mathematical subject, such as algebra equations (for example, Wolfram Mathematica{'}s FindEquationProof function \cite{Wolfram2019}) or geometrical theorems (for example, the Geometry Expert or GEX \cite{Gao1998} of Key Laboratory of Mathematics Mechanization, Chinese Academy of Sciences). Some relatively new works in this aspect includes Microsoft{'}s Lean prover \cite{Moura2021} and Z3 \cite{Moura2008} algorithm.

@@

Mainly developed in the twentieth century by the contribution of MacLane and Eilenberg with the purpose to investigate algebra topology, the category theory is a fast-evolving aspect of modern mathematics. In just a few decades, the category theory has become the standard and formal language of homology algebra and algebraic geometry and has gained a lot of meaningful achievements, for instance the Yoneda{'}s Lemma and Braid categories, which serves as a neat explanation for the Yang-Baxter Equation (YBE) \cite{Li2019}. Moreover, the category theory{'}s main idea, which is to put mathematical structures into categories satisfies the worldview of the Bourbaki school.

@@

\begin{equation*}
	f: A \to B
\end{equation*}
\begin{equation*}
	x\mapsto y
\end{equation*}

@@

To avoid misunderstandings, \textbf{the Zermelo-Fraenkel set theory} or ZFC as short is utilized to be the set system, with Grothendieck universe concepts added. \cite{Li2019}

@@

The definitions and theories presented in the paper utilizes the concepts of the category theory \cite{Li2019} and axiomatic set theory \cite{Li2019}. Therefore, readers are recommended to review understandings and conclusions about the two concepts before going over the paper.

@@

%%\pmb{ Theorem. }
\begin{theorem}
	The Zermelo{'}s Well-Ordering Theorem.\cite{Li2019}

@@

	The proof can be found in citation \cite{Li2019}.
\end{theorem}

Some preliminary knowledge also includes the Ebbinghaus Forgetting Curve equation \cite{Ebbinghaus1913} used in this paper later. This approximate function is defined below:

\begin{equation*}
	E(\mathit{t})=\frac{100 k}{(\ln  t)^c+k}
\end{equation*}

@@

So as to avoid utilization of impure functions, a pseudo random generator is used. We select the linear congruential generators \cite{Entacher1997}, whose recursive equation is,

\begin{equation*}
	X_{n+1}=(\left(a X_n+c\right) \bmod M)
\end{equation*}

@@

\begin{equation*}
	M=2^{32},a=1103515245, c=12345
\end{equation*}

@@

\section{The Computerized Representation of Mathem-atical Structures}

Before more specific discussion, we select Grothendieck universe \(\mathcal{U}\) \cite{Li2019} to avoid set theory paradoxes. Besides, we define meta category \(\mathcal{C}\) where all discussions take place. There are briefly three kind of objects in \(\mathcal{C}\): symbols, notations and brackets. All symbols in \(\mathcal{C}\) forms sub-category \(\text{Sym}(\mathcal{C})\) called the \textbf{ Symbol Subcategory}. All notations in \(\mathcal{C}\) forms \(\text{Not}(\mathcal{C})\) and all brackets forms \(\text{Bra}(\mathcal{C})\), called the \textbf{ Notation Subcategory} and the \textbf{ Bracket Subcategory}. That is,

\begin{equation}
	\mathcal{C}=\text{Sym}(\mathcal{C})\sqcup \text{Not}(\mathcal{C})\sqcup \text{Bra}(\mathcal{C})
\end{equation}

@@

	\begin{equation}
		\beta \text{:=}\left\{(i,x)\left|i\in \text{On}_{\geq 1}\right.,x\in \text{Sym}(\mathcal{C})\cup \text{Not}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\right\}
	\end{equation}

@@

	\begin{equation}
	\begin{split}
		\beta =\{(j,\mathcal{N})\}\cup \{(i,x)|i\in \text{On}_{\geq 1},\\ x\in \text{Sym}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\},\forall
		t\in \beta ,j\in \text{On}_{[1,t_{\ell }]}\}
	\end{split}
	\end{equation}
\end{definition}

@@

	\begin{equation}
		\begin{gathered}
			\mathit{p}:\text{Ob}(\text{Not}(\mathcal{C}))\to \text{On}_{\geq 0}\\
			\mathcal{N}\overset{\mathit{p}}{\mapsto}n
		\end{gathered}
	\end{equation}

@@

	\begin{equation}
		\begin{gathered}
			\nu :\text{Sym}(\mathcal{C})\to \text{Not}(\mathcal{C})\\
			\mathcal{S}\overset{\mathit{v}}{\mapsto }\nu (\mathcal{S})
		\end{gathered}
	\end{equation}

	\noindent where \(\nu (\mathcal{S})\) is the \textbf{ corresponding notation} of \(\mathcal{S}\) and must satisfy \(\forall \mathcal{S}\in \text{Sym}(\mathcal{C}),\mathit{p}(\nu (\mathcal{S}))\) \(= 0\), indicating all corresponding notations are types instead of operators. For convenience and precision, the text that meaning creating a symbol \(\mathcal{S}\) whose corresponding notation is \(\mathcal{N}\)can and should be written in the form below.

	\begin{equation}
		\mathcal{S}\in \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\mathcal{S})==\mathcal{N}
	\end{equation}

@@

	\begin{equation}
		\epsilon :\alpha \equiv \beta
	\end{equation}
\end{definition}

A bracket, in order to enhance simplicity, can be put into a symbol. Therefore with these three definitions, how do we actually represent mathematical stuff? One example is how to utilize them to express one of the most basic mathematical concepts, such as a single number 12. To complete this task, we may first define a notation Number and define a symbol \(\mathcal{S}_1\) whose corresponding notation is Number. Then, how do we determine the number is 12 instead of other numbers like 15? This can be solved using the ordinal theory we presented before in the Preliminary section.

@@

	\begin{equation}
		h\in \text{Mor}(\text{Not}(\mathcal{C})): \mathcal{M}\to \mathcal{N}
	\end{equation}

	It is obviously without any ambiguity that \(\forall \mathcal{M},\mathcal{N}\in \text{Not}(\mathcal{C}),\left|\text{Hom}_{\mathcal{C}}(\mathcal{M},\mathcal{N})\right|$ $\in \{0,1\}\). Moreover, if \(\mathcal{N}\) is a kind of \(\mathcal{M}\) then \(\mathit{p}(\mathcal{N})\geq \mathit{p}(\mathcal{M})\). For simplicity, \(\mathcal{N}\) is inherited from \(\mathcal{M}\) can be annotated as \(\mathcal{N}\triangleleft |\mathcal{M}\).
\end{definition}

@@

\begin{equation*}
	\sum _{n=0}^{\infty } x^n=\frac{1}{1-x}, \text{for} |x|<1
\end{equation*}

First, we need to observe what notation is needed by the construction. Apparently, we need to at least define these notations: \(\text{inf}\), \(\text{int}\), \(\text{num}\),\textit{  }\textit{ \(\sum\)}, \(=\), \({}^{\wedge}\), \(/\), \(-\), \(\text{abs}\), \(<\) and \(\text{for}\), where \(\text{abs}\) stands for the absolute value function. However, in this neat example, the concept of function is not needed to be defined. Additionally, as the constructed stuff only needs to demonstrate the equation itself instead of the principles behind the equality, there is no necessity for the definition of notation \(+\). Note that manifestly \(\text{int} \triangleleft | \text{num}\). The table below (\ref{table-1}) demonstrates the number of parameters taken by the notations.

\begin{table}
	\centering
	\label{table-1}
	\begin{tabular}{ccccccccccc}
		\toprule
		$\mathcal{N}$ & int & num & inf & $\sum$ & $=$ & $/$ & - & abs & $<$ & for \\
		\midrule
		$\mathit{p}$ & $0$ & $0$ & $0$ & $3$ & $2$ & $2$ & $2$ & $1$ & $2$ & $2$ \\
		\bottomrule
	\end{tabular}
	\caption{The table for $\mathit{p}(\mathcal{N})$}
\end{table}

@@

\begin{equation*}
	\begin{aligned}
		\pmb{1} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{1})=\text{number}\\
		\pmb{\infty } &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{\infty })=\text{infinity}\\
		\pmb{x} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{x})=\text{number}\\
		\pmb{n} &\in& \text{Ob}(\text{Sym}(\mathcal{C}))\land \mathit{v}(\pmb{n})=\text{integer}\triangleleft |\text{number}\\
	\end{aligned}
\end{equation*}
\begin{equation*}
	\begin{aligned}
		\alpha &=& \{(0,\text{for}),(1,\beta ),(2,\gamma )\}\\
		\beta &=& \{(0,=),(1,\delta ),(2,\epsilon )\}\\
		\gamma &=& \{(0,<),(1,\zeta ),(2,\pmb{1})\}\\
		\delta &=& \{(0,\sum ),(1,\eta ),(2,\pmb{\infty }), (3,\theta )\}\\
		\epsilon &=& \{(0,/),(1,\pmb{1}),(2,\iota )\}\\
		\zeta &=& \{(0,\text{abs}),(1,\pmb{x})\}\\
		\eta &=& \{(0,=),(1,\pmb{n}),(2,\pmb{1})\}\\
		\theta &=& \{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\}\\
		\iota &=& \{(0,-),(1,\pmb{1}),(2,\pmb{x})\}
	\end{aligned}
\end{equation*}

@@

\begin{equation}
	\begin{split}
	\alpha = \{(0,\text{for}),(1,\beta ),(2,\{(0,<),(1,\{(0,\text{abs}),\\(1,\pmb{x})\}),(2,\pmb{1})\})\}\hfill\\
	\beta = \{(0,=),(1,\delta ),(2,\{(0,/),(1,\pmb{1}),(2,\{(0,-),\\(1,\pmb{1}),(2,\pmb{x})\})\})\}\hfill\\
	\delta = \{(0,\sum ),(1,\{(0,=),(1,\pmb{n}),(2,\pmb{1})\}),(2,\pmb{\infty }), (3,\\\{(0,{}^{\wedge}),(1,\pmb{x}),(2,\pmb{n})\})\}\hfill\\
	\end{split}
\end{equation}

@@

	It is essential to pay attention to that a bracket with 2-parameter notation is not necessarily a micro-statement. This conclusion can be illustrated via the example of the bracket  \(\{(0,+),(1,x),(2,y)\}\) whose notation has two symbols as parameters but is not a micro-statement. The second restriction is more important, which is that a micro-statement must have the capacity to be evaluated into a Boolean value, that is, \(\text{true}\) or \(\text{false}\). What is notable, the \textbf{ evaluation} process is not declared inside the representation system, whose definition comes below. All micro-statement brackets forms the \textbf{ Micro-Statement }sub-category of \(\text{Bra}(\mathcal{C})\) and is annotated as \(\text{Mic}(\mathcal{C})\).
\end{definition}

@@

	\begin{equation}
		\begin{gathered}
			\mathit{e}\mathit{v}\mathit{a}\ell :\text{Ob}(\text{Mic}(\mathcal{C}))\to \mathcal{B}\\
			\mathit{m}\overset{\mathit{e}\mathit{v}\mathit{a}\ell }{\mapsto }\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})
		\end{gathered}
	\end{equation}

@@

\begin{equation}
	\forall \alpha ,\beta \in \text{Ob}(\text{Mic}(\mathcal{C})), \forall \left|\text{Hom}_{\text{Mic}(\mathcal{C})}(\alpha ,\beta )\right|=1
\end{equation}

@@

	\begin{equation}
		\mathcal{D}\text{:=}\left\{\left(i,\mathcal{M}_i\right)|i\in \text{On}_{\geq 1}\right\}
	\end{equation}

@@

	\begin{equation}
		\left(i,\mathcal{M}_i\right)\overset{\mathit{s}\mathit{t}\mathit{e}\mathit{p}}{\mapsto }\left(i+1,\mathcal{M}_{i+1}\right)
	\end{equation}

@@

	\begin{equation}
		\mathcal{M}_{i+1}=\mathcal{F}_i\mathcal{M}_i
	\end{equation}
\end{definition}

@@

	\begin{equation}
		\exists n\in [0,\omega ), \mathcal{R}\subseteq \text{Ob}\left(\mathcal{M}_n\right)
	\end{equation}

@@

	\begin{equation}
		\begin{gathered}
			\sigma =T(\mathcal{K})_{\ell }\\
			\tau =T(\mathcal{K})_{\mathit{r}}
		\end{gathered}
	\end{equation}
\end{definition}

@@

	\begin{equation}
		\text{Ts}\text{:=}\left\{t\in \mathcal{M}_i|t\simeq T(\mathcal{K})_{\ell }\right\}
	\end{equation}
\end{definition}

@@

	\begin{equation}
		\begin{gathered}
			\mathcal{T}:\alpha _{\mathcal{B}}\cup \alpha _{\mathcal{S}}\to \beta _{\mathcal{B}}\cup \beta _{\mathcal{S}}\\
			\mathcal{S}_1\overset{\mathcal{T}}{\mapsto }\mathcal{S}_2
		\end{gathered}
	\end{equation}

@@

	\begin{equation}
		(\mu ')_{\mathcal{B}}\cup (\mu ')_{\mathcal{S}} =\mathcal{T}^{-1}\left(\mu _{\mathcal{B}}\cup \mu _{\mathcal{S}}\right)
	\end{equation}

	And then micro-statement \(\mu '\) is the freshly baked result of derivation. All of the micro-statements as results of map \(\mathcal{T}^{-1}\) forms new set \(\mathcal{M}'\). In the end we process the pool \(\mathcal{M}\) with this union operation:

@@

	\begin{equation}
		\begin{gathered}
			\mathcal{K}_n\overset{k_n}{\to }\mathcal{K}_{n+1}, n\in \mathbb{Z}_{[0,N-1]}\\
			\mathcal{K}_N\overset{k_N}{\to }\mathcal{K}_0
		\end{gathered}
	\end{equation}

Graphically, figure \ref{figure-1} illustrates the initial map.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}[commutative diagrams/every diagram]
		\node (K0) at (90:2.3cm) {$\mathcal{K}_0$};
		\node (K1) at (90+72:2cm) {$\mathcal{K}_1$};
		\node (K2) at (90+2*72:2cm) {$\mathcal{K}_2$};
		\node (K3) at (90+3*72:2cm) {$\mathcal{K}_3$};
		\node (Kn) at (90+4*72:2cm) {$\mathcal{K}_N$};

@@

		\path[commutative diagrams/.cd, every arrow, every label, dashed]
		(K3) edge node {$K_3$} (Kn)
		(Kn) edge node {$k_N$} (K0);
\end{tikzpicture}
	\caption{The initial map.}
	\label{figure-1}
\end{figure}

@@

	\begin{equation}
		w = k_j\left(\mathcal{K}_j\right)
	\end{equation}

@@

	\begin{equation}
		w = (\mathit{r} \bmod \sum _{u=0}^N )\left|\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_j,\mathcal{K}_q\right)\right|
	\end{equation}

	It is easy to understand that for each reflection functor \(\mathcal{K}_a\) and \(\mathcal{K}_b\), the count of set \(\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_a,\mathcal{K}_b\right)\) indicates the \textbf{ weight} of \(\mathcal{K}_b\) to \(\mathcal{K}_a\), controlling the probability of \(\mathcal{K}_b\) to be selected when the former functor is \(\mathcal{K}_a\). The design of this process is inspired by the lottery scheduling algorithm I learned in Andrew S. Tanenbaum{'}s Operating Systems: Design and Implementation \cite{Tanenbaum2015} before.
\end{definition}

An issue that worth attention is that as the random generator is defined as the following recursion formula: \cite{Entacher1997}

\begin{equation*}
	X_{n+1}=(\left(1103515245 X_n+12345\right) \bmod 2^{32})
\end{equation*}

Then each \(\mathit{r}\) must belongs to region \(\mathbb{Z}_{\left.\left[0,2^{32}\right.\right)}\). That is, obviously, if the count of all morphisms is more than $2^32$, then there will be some of the functors that will never be referred to, although there do exist morphisms targeting them. While in this paper the problem will not be solved and we assume that the number of the morphisms added up is smaller than the boundary of \(2^{32}\), which equals to four giga bytes and will not be exceeded in most engineering situations. Obviously although using the portable recursion equation the quality of the random numbers generated may be lower than nowadays{'} some technical implementations, it can be conveniently expressed in this paper. If the algorithm is implemented into the read world, a randomness collector, which generates random numbers from the real world, for example, the vibration of the computer motherboard, will probably act as a better solution.

The more detailed explanation of the recursive functor can be found in the algorithm below (Algorithm 1).

\begin{algorithm}[h!]
	\caption{Pseudo code for recursive functor $\mathcal{F}_t$}
	\begin{algorithmic}[1]
		\Require Pool $\mathcal{M}_{t}$, Knowledge base $\mathcal{Q}$, random $\mathit{r}$, Just used reflection functor index $i$
		\Ensure Next pool $\mathcal{M}_{t+1}$
